### 2018-07-17 latex/header.tex
Solved all todos :)
Incorporated changes by Toni
Some minor changes

To better understand these evolutionary changes and the role of NNMT for NAD metabolism, we built a mathematical model of the pathway using available enzyme kinetics data. Our simulations indicate that NNMT is required to maintain high NAD consumption fluxes, thereby enabling diversification of the NAD-dependent signalling pathways. This kinetic regulation requires and explains the unusually high substrate affinity of the key enzyme for Nam salvage, NamPRT. Moreover, we suggest that NNMT exerted evolutionary pressure on NamPRT, enforcing the development of its high substrate affinity. Using multiple sequence alignments, we identified a sequence insertion, first occurring in vertebrates, that parallels an experimentally verified increase in the substrate affinity of the enzyme. Additional simulations show that the deamidation pathway became obsolete owing to the high substrate affinity of NamPRT. Collectively, our results illustrate a close evolutionary relationship between NAD biosynthesis and the diversification of NAD-dependent signalling pathways, potentially driven by the concomitant occurrence of a regulator of Nam salvage, NNMT.

\section*{Keywords}

>>>>

To better understand these evolutionary changes and the role of NNMT for NAD metabolism, we built a mathematical model of the pathway using available enzyme kinetics data. Our simulations indicate that NNMT is required to maintain high NAD consumption fluxes, thereby enabling diversification of the NAD-dependent signalling pathways. This kinetic regulation requires and explains the unusually high substrate affinity of the key enzyme for Nam salvage, NamPRT. Moreover, we suggest that NNMT exerted evolutionary pressure on NamPRT, enforcing the development of its high substrate affinity. Using multiple sequence alignments, we identified a sequence insertion first occurring in vertebrates that parallels an experimentally verified increase in the substrate affinity of the enzyme. Additional simulations show that the deamidation pathway became obsolete owing to the high substrate affinity of NamPRT. Collectively, our results illustrate a close evolutionary relationship between NAD biosynthesis and the diversification of NAD-dependent signalling pathways, potentially driven by the concomitant occurrence of a regulator of Nam salvage, NNMT.

%\section*{Keywords}
